\sysfull

### 2018-04-14 paper/newCoalescing.tex
slow colaescing figure wrapped
intro colaescing figure wrapped

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/coal_Intro_Figure.pdf}%coalescing_timeline
	\caption{ When $N$ tasks coalesced $N-1$ commit operations is skipped.}
	\label{fig:coalIntro}
\end{figure}

@@

\subsubsection{SC: Slow Coalescing}
\label{subsec:slowCoalescing}

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/slowCoal}%coalescing_timeline
	\caption{The Slow coalescing algorithm \emph{linearly} updates its coalescing target}
	\label{fig:slowCoal}
\end{figure}

@@

\subsubsection{EC: Energy-aware Coalescing}
\label{subsec:ECoalescing}

>>>>

\begin{wrapfigure}{t!}{0.5\textwidth}
	\centering
	\includegraphics[width=0.5\columnwidth]{figures/coal_Intro_Figure.pdf}
	\caption{When $N$ tasks coalesced $N-1$ commit operations are skipped.}
	\label{fig:coalIntro}
\end{wrapfigure}

@@

\subsubsection{Slow Coalescing}
\label{subsec:slowCoalescing}

\begin{wrapfigure}{t!}{0.5\textwidth}
	\centering
	\includegraphics[width=0.5\columnwidth]{figures/slowCoal}
	\caption{The {\em slow coalescing} algorithm \emph{linearly} updates its coalescing target.}
	\label{fig:slowCoal}
\end{wrapfigure}

@@

\subsubsection{Energy-aware Coalescing}
\label{subsec:ECoalescing}
